Longitudinal Principal Manifold Estimation

### 2024-06-05 paper/main.tex
Updates from Overleaf

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{sim_case1}
  \includegraphics[width=\textwidth]{sim_case5}
  \caption{Scatterplots of two example simulated data clouds (gray points) with $d=1$ overlaid true embedding manifold (red), the estimated LMPE function (blue, dashed), PME (green, dotted), and principal curve or surface (purple, dot-dashed).}
  \label{fig:sim_case1}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{sim_case7}
  \caption{Scatterplots of two example simulated data clouds (gray points) with $d=2$ overlaid true embedding manifold (red), the estimated LMPE function (blue, dashed), PME (green, dotted), and principal curve or surface (purple, dot-dashed).}
  \label{fig:sim_case6}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{sim_case1}
  \includegraphics[width=\textwidth]{sim_case7}
  \caption{Scatterplots of two example simulated data clouds (gray points) with $d=1$ and $d=2$ overlaid with points on the true embedding manifold (red), the estimated LMPE function (blue), PME (green), and principal curve or surface (purple).}
  \label{fig:sim_results}
\end{figure}
